---
title: ""
output:
   
  html_notebook: 
    code_folding: none
    fig_caption: yes
    df_print: tibble
    toc: yes
    toc_float: 
       collapsed: true
       smooth_scroll: true
    #includes:
# bibliography: G:/CPHSS/OpenScience/WriteUps/aim1SurveyPaper/ReproSurveyPaper_02122018.bibtex
# csl: G:/CPHSS/OpenScience/WriteUps/aim1SurveyPaper/american-medical-association-no-url.CSL
---
<!-- <head{#top}> -->

<!-- <script src = "Main.js"></script> -->
<!-- <link rel="stylesheet" type="text/css" href="MainStyle.css"> -->
```{r, echo=FALSE}
htmltools::includeHTML("Navbar.html")
```
<BR><BR><img class="logo" src = "logo-header-stats.gif">
   
<!-- </head> -->

```{r setupOpts, echo=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, warning=FALSE, message=FALSE)
# Don't set echo to false for the overall options - r code chunks below need to appear
```

The resources listed on this page are sole-authored or have a lead author who is a woman, person of color, or both.

## Analysis of variance (ANOVA)

<a href="http://umanitoba.ca/faculties/health_sciences/medicine/units/chs/faculty_and_staff/7879.html">Lix, Lisa M.</a>, Keselman, Joanne C., & Keselman, H. J. (1996). <a href = "https://www.jstor.org/stable/1170654?seq=1#metadata_info_tab_contents">Consequences of assumption violations revisited: A quantitative review of alternatives to the one-way analysis of variance F test.</a> Review of Educational Research, 66(4), 579–619.

<a href="https://www.linkedin.com/in/mary-mchugh-35134932/">McHugh, Mary L.</a> (2011). <a href = "https://hrcak.srce.hr/file/108599">Multiple comparison analysis testing in ANOVA.</a> Biochemia medica: Biochemia medica, 21(3), 203-209.

## Chi-squared

<a href ="https://asianmideast.duke.edu/people/hae-young-kim">Kim, Hae-Young</a>. (2017). <a href = "https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5426219/"> Statistical notes for clinical researchers: Chi-squared test and Fisher’s exact test.</a> Restorative Dentistry & Endodontics, 42(2), 152–155.

<a href="https://www.linkedin.com/in/mary-mchugh-35134932/">McHugh, Mary L.</a> (2013). <a href ="https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3900058/">The chi-square test of independence.</a> Biochemia Medica, 23(2), 143–149.

## Choosing a statistical test

McCrum-Gardner, E. (2008). Which is the correct statistical test to use? British Journal of Oral and Maxillofacial Surgery, 46(1), 38–41.

## Cluster analysis

Altman, N. S., & Krzywinski, M. (2017). Points of Significance: Clustering. Nature methods, 14(6), 545-546. https://doi.org/10.1038/nmeth.4299

## Correlation

Mukaka, M. M. (2012). A guide to appropriate use of correlation coefficient in medical research. Malawi Medical Journal, 24(3), 69–71.

David, F. N. (1938). Tables of the correlation coefficient. In Tables of the ordinates and probability integral of the distribution of the correlation coefficient in small samples (Biometrika Trust) (pp. 44–59). Cambridge, UK: Cambridge University Press.

## Descriptive statistics

<a href="https://www.linkedin.com/in/mary-mchugh-35134932/">McHugh, Mary L.</a> and Villarruel, A.M. (2003), <a href="https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1744-6155.2003.tb00182.x">Descriptive Statistics, Part I: Level of Measurement.</a> Journal for Specialists in Pediatric Nursing, 8: 35-37. doi:10.1111/j.1744-6155.2003.tb00182.x

<a href="https://www.linkedin.com/in/mary-mchugh-35134932/">McHugh, Mary L.</a> and Hudson‐Barr, D. (2003),<a href="https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1088-145X.2003.00111.x"> Descriptive Statistics, Part II: Most Commonly Used Descriptive Statistics.</a> Journal for Specialists in Pediatric Nursing, 8: 111-116. doi:10.1111/j.1088-145X.2003.00111.x

## Effect sizes

Mays, M. Z., & Melnyk, B. M. (2009). A call for the reporting of effect sizes in research reports to enhance critical appraisal and evidence-based practice. Worldviews on Evidence-Based Nursing, 6(3), 125–129.

## Linear models / Regression

Norris, C. M., Ghali, W. A., Saunders, L. D., Brant, R., Galbraith, D., Faris, P., & Knudtson, M. L. (2006). Ordinal regression model and the linear regression model were superior to the logistic regression models.Journal of Clinical Epidemiology, 59(5), 448–456.

## Kappa

<a href="https://www.linkedin.com/in/mary-mchugh-35134932/">McHugh, Mary L.</a> (2012). <a href="https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3900052/">Interrater reliability: the kappa statistic.</a> Biochemia medica, 22(3), 276–282.

## Kurtosis

<a href ="https://asianmideast.duke.edu/people/hae-young-kim">Kim, Hae-Young</a>. (2013). Statistical notes for clinical researchers: Assessing normal distribution (2) using skewness and kurtosis. Restorative Dentistry & Endodontics, 38(1), 52–54.

## Network analysis

Harris, Jenine K. (2013). <a href = "https://us.sagepub.com/en-us/nam/an-introduction-to-exponential-random-graph-modeling/book237737">An introduction to exponential random graph modeling (Vol. 173).</a> Sage Publications.

## Normal distribution

<a href ="https://asianmideast.duke.edu/people/hae-young-kim">Kim, Hae-Young</a>. (2013). Statistical notes for clinical researchers: Assessing normal distribution (2) using skewness and kurtosis. Restorative Dentistry & Endodontics, 38(1), 52–54.

## p-values

Altman, N., & Krzywinski, M. (2017). Points of Significance: Interpreting P values. Nature methods, 14(3), 213-214. https://doi.org/10.1038/nmeth.4210

## Research quality

García-Berthou, E., & Alcaraz, C. (2004). Incongruence between test statistics and p values in medical papers. BMC Medical Research Methodology,
4(13). Retrieved from https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/1471-2288-4-13

Nuijten, M. B., Hartgerink, C. H. J., Assen, M. A. L. M., Epskamp, S., & Wicherts, J. M. (2015). The prevalence of statistical reporting errors in psychology (1985–2013). Behavior Research Methods, 48(4), 1205–1226.

## Sample size

Box, J. F. (1987). Guinness, Gosset, Fisher, and small samples. Statistical Science, 2(1), 45–52.

## Skewness 

<a href ="https://asianmideast.duke.edu/people/hae-young-kim">Kim, Hae-Young</a>. (2013). Statistical notes for clinical researchers: Assessing normal distribution (2) using skewness and kurtosis. Restorative Dentistry & Endodontics, 38(1), 52–54.

## Statistics books 

Garner, R. (2010). The joy of stats: A short guide to introductory statistics in the social sciences. Toronto: University of Toronto Press.

Harris J.K. (2020). Statistics with R: Solving Problems Using Real World Data. Thousand Oaks, CA: Sage. 

## t-tests

Delacre, M., Lakens, D., & Leys, C. (2017). Why psychologists should by default use Welch’s t-test instead of Student’s t-test. International Review of Social Psychology, 30(1), 92–101. doi: http://doi.org/10.5334/irsp.82

Connelly, L. M. (2011). t-tests. Medsurg Nursing, 20(6), 341.

## Transformation

Manikandan, S. (2010). Data transformation. Journal of Pharmacology and Pharmacotherapeutics, 1(2), 126–127.

## Visual display of data / graphs 

Brasseur, L. (2005). Florence Nightingale’s visual rhetoric in the rose diagrams. Technical Communication Quarterly, 14(2), 161–182.
